Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-10-11 methods_paper/fabl-paper.tex
update.

We calculate a Bayes estimate \(\hat{\mathbf{Z}}\) for the linkage
parameter \(\mathbf{Z}\) by assigning different positive losses to
different types of errors, and minimizing posterior expected loss. We
adopt the loss function proposed in Sadinle 2017, in which
\(\hat{Z}_j \in \{1, \ldots, n_A + 1, R\}\), with \(R\) representing the
option to leave the matching undetermined by the model. Specifically, we have

@@

In this section, we replicate a simulation study from \cite{sadinle2017} to compare \texttt{fabl} against \texttt{BRL} on several simulated datasets with varying amounts of error and overlap. We use first name, last name, age, and occupation for this linkage, and create comparison vectors according to the default settings of the \texttt{compareRecords} function from the \texttt{BRL} package. See Table~\ref{Tab:sadinle_simulation_cutoffs} for details on the construction of comparison vectors. Each simulation identifies duplicated individuals between two datasets, each with 500 records. We conduct linkage when matching records exhibit 1, 2, and 3 errors across the four fields, and when there are 50, 250, and 450 individuals in common across datasets. We use flat priors for all $m$ and $u$ parameters, run the Gibbs Sampler for 1000 iterations, and discard the first 100 as burn-in.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot2} 
\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from Sadinle 2017. For each level of overlap and each level of error, we have 100 paired sets of 500 records.}
\label{fig:sadinle_simulation}
\end{center}
\end{figure}

>>>>

We calculate a Bayes estimate \(\hat{\mathbf{Z}}\) for the linkage
parameter \(\mathbf{Z}\) by assigning different positive losses to
different types of errors, and minimizing posterior expected loss. We
adopt the loss function proposed in \cite{sadinle_bayesian_2017}, in which
\(\hat{Z}_j \in \{1, \ldots, n_A + 1, R\}\), with \(R\) representing the
option to leave the matching undetermined by the model. Specifically, we have

@@

In this section, we replicate a simulation study from \cite{sadinle_bayesian_2017} to compare \texttt{fabl} against \texttt{BRL} on several simulated datasets with varying amounts of error and overlap. We use first name, last name, age, and occupation for this linkage, and create comparison vectors according to the default settings of the \texttt{compareRecords} function from the \texttt{BRL} package. See Table~\ref{Tab:sadinle_simulation_cutoffs} for details on the construction of comparison vectors. Each simulation identifies duplicated individuals between two datasets, each with 500 records. We conduct linkage when matching records exhibit 1, 2, and 3 errors across the four fields, and when there are 50, 250, and 450 individuals in common across datasets. We use flat priors for all $m$ and $u$ parameters, run the Gibbs Sampler for 1000 iterations, and discard the first 100 as burn-in.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot2} 
\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from \cite{sadinle_bayesian_2017}. For each level of overlap and each level of error, we have 100 paired sets of 500 records.}
\label{fig:sadinle_simulation}
\end{center}
\end{figure}
